Measuring E-Mail Header Injections on the World Wide Web

### 2016-10-25 Discussion/mitigation.tex
brought it down to 10
9.75

Using a safe, well tested \email library is the preferred way of
preventing \ehi vulnerabilities (removing the burden of input
sanitization from the developer). A list of known secure libraries for
each language and framework discussed is shown in
Table~\ref{tab:maillib}.

	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of \ehi vulnerability.
	\begin{table}[tbp]
		\centering
		\scriptsize
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website:\\ https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
			\hline
			Python & SMTPLib with email.header.Header\tablefootnote{instead of using email.parser.Parser to parse the header}\\
			\hline
			Java & Apache Commons E-Mail\tablefootnote{Apache Commons E-Mail: https://commons.apache.org/proper/commons-email/}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\tablefootnote{Ruby Mail Website: https://rubygems.org/gems/mail}\\
			\hline
			WordPress & Contact Form 7\tablefootnote{Contact Form 7 Download: https://wordpress.org/plugins/contact-form-7/}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
		\label{tab:maillib}
	\end{table}

>>>>

Using a safe, well tested \email library is the preferred way of
preventing \ehi vulnerabilities (removing the burden of input
sanitization from the developer). A list of known secure libraries for
each language and framework discussed is shown in
Table~\ref{tab:maillib}.
	\begin{table}[tbp]
		\centering
		\scriptsize
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\cite{Hagenbuch2016}, PHPMailer\cite{PHPMailer2016}, Swiftmailer\cite{SwiftMailer2016}}}\\
			\hline
			Python & SMTPLib with email.header.Header\\
			\hline
			Java & Apache Commons E-Mail\cite{ACE2016}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\cite{RubyMailGem2016}\\
			\hline
			WordPress & Contact Form 7\cite{CF7}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
		\label{tab:maillib}
	\end{table}

### 2016-10-25 Results/virus_data.tex
9.75

\subsection{Emails with Malicious Attachments}
We checked the \emails received by the `reguser' account (which are injected with regular \email addresses and not malicious data) for the presence of attachments that may contain malicious software, which will indicate that the server itself is not benign.

>>>>

\subsection{Emails with Malicious Attachments}
As additional analysis to find malicious attachments, we checked the \emails received by the `reguser' account (which are injected with regular \email addresses and not malicious data) for the presence of attachments that may contain malicious software, which will indicate that the server itself is not benign.

### 2016-10-25 System/components.tex
9.75

The Data Gathering module and Payload Injection modules are composed of smaller components. This section describes the functionality of each of the components.

\subsubsection{Crawler}
\label{Comp:Crawler}
We used an open-source Apache Nutch based Crawler~\cite{nutch}. The Crawler continuously crawls the web. The Crawler provides the system with a continuous feed of URLs and the HTML contained in those pages.

\subsubsection{Form Parser}
\label{Comp:FP}
The actual analysis pipeline begins at the Form Parser. This module is
responsible for parsing the HTML and retrieving data about the HTML
forms on the page, including the following: (1) Form attributes, such
as \texttt{method} and \texttt{action} (URL) for the HTTP request, (2)
Data about the form input fields, such as their attributes, names, and
default values. The default values are essential for fields like
{\lstinline{<input type="hidden">}} as these fields are usually used
to check for the submission of forms by bots, and (3) Presence of the {\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted (if the \texttt{action} attribute is a relative URL).
      % Adam: this is not correct, the referrer header won't be used when we make the request. We will set the referrer header when we make the request to URL that the form is on
	%% \item Headers associated with the page, such as \texttt{referrer}. Once again, these were required to avoid the website from ignoring our system as a bot.

\subsubsection{\Email Field Checker}
\label{Comp:EMFC}
The \Email Field Checker is the final stage in the Data Gathering module. It receives the output of the previous stage---HTML form data---and checks for the presence of \email fields in those forms. If any \email fields are found, it stores references to these forms.
The intuition here is that we do not want to try to fuzz all HTML forms on the web to look for \ehi vulnerabilities, rather just those HTML forms that are likely to invoke server-side email functionality.

@@

\noindent\textbf{Non-Malicious Payload.}
The regular or non-malicious payload is simply an \email address. The goal is to see if the web application will send an \email message based on our input. The specific format of the \email is \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.

@@

	This payload is the most minimal payload: it injects a newline character followed by the \texttt{bcc} field.

@@

	As discussed previously, the addition of the \texttt{x-check:in} header is to inject Python-based web applications.

@@

Payloads 3 and 4 are added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.~\cite{rfc2616}

\end{enumerate}
The \texttt{(xxxx)} in each payload is replaced by an internal unique id to create a one-to-one mapping of the payloads to the forms.
% Adam: If we need to cut things for space, we can cut this next line and the payload coverage table.

@@

\noindent\textbf{Analyzing \email with payloads}
The ``\emails with payloads'' refers to \emails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts. These \emails could only be received as a result of injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer}.

>>>>

The Data Gathering module and Payload Injection modules are composed of smaller components. This section describes the functionality of those components.

\subsubsection{Data Gathering}
\label{Comp:Crawler}
We used an open-source Apache Nutch based Crawler~\cite{nutch}. The \texttt{Crawler} provides the system with a continuous feed of URLs and the HTML contained in those pages. 
\label{Comp:FP}
The \texttt{Form Parser} is responsible for parsing the HTML and retrieving data about the HTML
forms on the page, including the following: (1) Form attributes, such
as \texttt{method} and \texttt{action} (URL) for the HTTP request, (2)
Data about the form input fields, such as their attributes, names, and
default values. The default values are essential for fields like
{\lstinline{<input type="hidden">}} as these fields are usually used
to check for the submission of forms by bots, and (3) Presence of the {\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted (if the \texttt{action} attribute is a relative URL).

\label{Comp:EMFC}
The \texttt{\Email Field Checker} is the final stage in the Data Gathering module. It receives the HTML form data and checks for the presence of \email fields in those forms. If any \email fields are found, it stores references to these forms.
The intuition here is that we do not want to try to fuzz all HTML forms on the web to look for \ehi vulnerabilities, rather just those HTML forms that are likely to invoke server-side email functionality.

@@

\noindent\textbf{Non-Malicious Payload.}
The regular or non-malicious payload is simply an \email address. The goal is to see if the web application will send an \email message based on our input. The specific format of the \email is \lstinline|reguser(xxxx)@example.com|, where \texttt{xxxx} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.

@@

@@

@@

\end{enumerate}
Payload 1 is the most minimal payload: it injects a newline character followed by the \texttt{bcc} field. Payload 2 contains the additional \texttt{x-check} header to inject Python-based web applications. Payloads 3 and 4 are added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.~\cite{rfc2616}

The \texttt{(xxxx)} in each payload is replaced by an internal unique id to create a one-to-one mapping of the payloads to the forms.
% Adam: If we need to cut things for space, we can cut this next line and the payload coverage table.

@@

\noindent\textbf{Analyzing \email with payloads}
The ``\emails with payloads'' refers to \emails received by either the {\lstinline{nuser(xxxx)@example.com}} or {\lstinline{maluser(xxxx)@example.com}} accounts. These \emails could only be received as a result of injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer}.

### 2016-10-25 introduction.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.
9.75

\ehi vulnerabilities are a lesser-known command injection vulnerability\footnote{\ehi can be considered as the \email equivalent of HTTP Header Injection~\cite{wiki:HTTP_headerinjection}}. We verified that this vulnerability exists in the implementation of the built-in \email functionality in the popular languages PHP, Java, Python, and Ruby. The format of \email messages is defined by the Simple Mail Transfer Protocol (SMTP)~\cite{rfc5322}. Each \email message is represented by a series of headers separated by newlines, followed by the body content (separated from the headers by two newlines). Some of these headers are mandatory (From, To, Date), but the headers could also include other information such as the Subject, CC, BCC, etc.

@@

The objective of our research is to study the prevalence of this vulnerability on the World Wide Web and identify whether further research is required in this area.
\\

\noindent{}In summary, we make the following contributions:
\begin{itemize}

>>>>

\ehi vulnerabilities are a lesser-known command injection vulnerability. We verified that this vulnerability exists in the implementation of the built-in \email functionality in the popular languages PHP, Java, Python, and Ruby. The format of \email messages is defined by the Simple Mail Transfer Protocol (SMTP)~\cite{rfc5322}. Each \email message is represented by a series of headers separated by newlines, followed by the body content (separated from the headers by two newlines). Some of these headers are mandatory (From, To, Date), but the headers could also include other information such as the Subject, CC, BCC, etc.

@@

The objective of our research is to study the prevalence of this vulnerability on the World Wide Web and identify whether further research is required in this area.
In summary, we make the following contributions:
\begin{itemize}
